\documentclass[12pt,twoside]{article}

\usepackage{geometry}
\usepackage{resume}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
% \usepackage{tgtermes}

\begin{document}

\topheading
    {Adam Blackwater}
    {me@adamblackwater.com}
    {07722-432-866}
    {www.github.com/adam-blackwater}
    {www.adamblackwater.com}
    {www.linkedin.com/in/adam-blackwater}

\vspace{1.0em}
\hrule
\vspace{1.2em}

\statement
    {Personal Statement}
    {
        Software engineer with professional experience in back-end software
        development, and a Computer Science background. 

        \hspace{1.5em}Worked across teams to deliver public facing code and
        internal tools. Effective team member, thoroughly enjoy the
        collaborative aspect of software development.
    }

\vspace{1.2em}
\hrule
\vspace{1.2em}

\noindent{\textbf{Skills}}
\begin{center}
    \begin{tabular}{l l l l l l l}
        SQL & REST & AWS/GCP & cURL & Python & Redis & Micro services \\
        Git & TDD & CI/CD & Linux & atiohttp & Postgres & API desing \& documentation \\
        SSH & Java & Kubernetes & HTTP & PyTest& Docker & Pair programming
    \end{tabular}
\end{center}

\vspace{0.4em}
\hrule
\vspace{1.2em}

\headedsection
    {Work Experience}
    {
        \textbf{WayHome} | Back-End Software Engineer}
    {
        Developed containerised micro-services orchestrated using Kubernetes. Wrote
        services for consumption by the data team to aid in creating data models.

        \hspace{1.5em}Integrated third-party RESTful API's and wrote a service to
        automate a business process, freeing up valuable customer facing
        employee time.
    }

\vspace{1.2em}
\hrule
\vspace{1.2em}

\headedsection
    {Education}
    {
        \textbf{Computer Science; First-class honours} | The University
        Greenwich - 2019
    }
    {
        Won lead student representative role in first year. Chaired meetings,
        and took sole responsibility of producing a document for review by
        senior staff and external observers.
    }

\vspace{1.2em}
\hrule
\vspace{1.2em}

\headedsection
    {Projects}
    {\textbf{A Chess Portable-Game-Notation (PGN) Analysis Tool} | \textit{Rust}}
    {
        $\triangleright$ Command line program that iterates over PGN files in a
        directory. \\
        $\triangleright$ Parses PGN files and returns win/loss/draws against
        opening moves played. \\
        $\triangleright$ Used TDD throughout development. \\
        $\triangleright$ Learnt Rust while developing this tool.
    }

\vspace{0.3em}

\headedsection
    {}
    {\textbf{Open Risk} | \textit{Python - aiohttp - MySql}}
    {
        $\triangleright$ Collaborating with others developers remotely \\
        $\triangleright$ Writing asynchronous Python code \\
        $\triangleright$ Graph data structure for data modelling
    }

\vspace{0.3em}

\headedsection
    {}
    {\textbf{Optimisation and Scheduling Software} | \textit{thesis}}
    {
        $\triangleright$ TTD based project using OOP principals. Used the MVC
        design pattern. Made use of the Flask framework for front-end, and
        Python for the back-end. \\
        $\triangleright$ Applied a genetic combinatorial optimisation algorithm
        to optimise a scheduling problem. \\
        $\triangleright$ System read/writes MySQL database. Queries database,
        result given to algorithm to automate schedule creation.
    }

%\vspace{1.2em}
%\hrule

\end{document}

        %Product minded software engineer writing well tested code. Experience
        %writing RESTful APIs in Node.js + express, Python + Flask, and
        %using testing libraries.

        %\hspace{2.0em}Graduated with a first-class honours degree in Computer
        %Science at the end of 2019. Self-motivated and eager to turn my
        %experience of software engineering into products that create value for
        %both company and end user.

%\begin{center}
%        \begin{tabular}{c c}
%                Analytical Methods: \textbf{87\%} &
%                Artificial Intelligence: \textbf{83\%} \\
%                Advanced Programming: \textbf{82\%} &
%                Application and Web Development: \textbf{89\%} \\
%                Networking and Operating Systems: \textbf{99\%} &
%                Programming Distributed Components: \textbf{86\%} 
%        \end{tabular}
%\end{center}
