\documentclass[12pt,twoside]{article}

\usepackage{geometry}
\usepackage{resume}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\textheight=900pt

\begin{document}

\topheading
    {Adam Blackwater}
    {\url{me@adamblackwater.com} \hspace{0.15em}}
    {\url{www.github.com/adam-blackwater}}
    {\url{www.adamblackwater.com}}
    {\url{www.linkedin.com/in/adam-blackwater}}
    {07722--432--866}

\vspace{0.5em}
\hrule
\vspace{0.5em}

\statement
    {Personal Statement}
    {
        Software engineer with professional experience in back-end software
        development, and a university degree in Computer Science. Currently
        looking for a new role after previous employer ran out of money.

        \hspace{1.5em}Effective team member. Proven ability to deliver well
        tested code both independently and via pair programming. 

        \hspace{1.5em}Product minded and focused on using my technical knowledge 
        to create value for both business and users.
    }

\vspace{0.5em}
\hrule
\vspace{0.5em}

\noindent{\textbf{Skills}}
\begin{center}
    \begin{tabular}{l l l l l l l}
        SQL & REST & AWS/GCP & cURL & Python & Redis & Micro services \\
        Git & TDD & CI/CD & Linux & aiohttp & Postgres & API design \& documentation \\
        SSH & Java & Kubernetes & HTTP & PyTest& Docker & Pair programming
    \end{tabular}
\end{center}
    
\parbox{35em}{
    $\triangleright$ Main project maintainer for open source Risk clone \\
    $\triangleright$ Designed and implemented Risk clone APIs from scratch \\
    $\triangleright$ Used Docker to build micro-services based Risk project \\
    $\triangleright$ Strong organisational skills developed while working in my family's business \\
    $\triangleright$ Proven to be a reliable team member and able to bring out the best in my team
    }

\vspace{0.5em}
\hrule
\vspace{0.5em}

\headedsection
    {Experience}
    {
        \textbf{WayHome} | Junior Back-End Software Engineer}
    {
        $\triangleright$ Experience writing containerised micro-services
        orchestrated using Kubernetes. \\
        $\triangleright$ Proficient in using TDD in a professional setting \\
        $\triangleright$ Integrated third-party RESTful API's to automate business processes \\
        $\triangleright$ Well versed in CI/CD \\
        $\triangleright$ Experienced in pair programming
    }

\vspace{0.5em}
\hrule
\vspace{0.5em}

\headedsection
    {Education}
    {
        \textbf{Computer Science; First-class honours | The University
        Greenwich: 2015--2019}
    }
    {
        $\triangleright$ Studied low level concepts (mathematical logic)
        through to high level concepts \\
        $\triangleright$ Implemented a genetic combinatorial optimisation
        algorithm for thesis project \\
        $\triangleright$ Won lead student representative role first year
        Chaired meetings, wrote a student review of the college for review by
        external observers \\
        $\triangleright$ Worked on group web development projects to tight deadlines
    }

\vspace{0.5em}
\hrule
\vspace{0.5em}

\headedsection
    {Projects}
    {\textbf{Open Risk} | \url{www.github.com/open-risk-game} | \textit{Currently The Main Maintainer}}
    {
        $\triangleright$ Collaborating remotely and asynchronously with other developers \\
        $\triangleright$ Experience using Git to work effectively with colleagues \\
        $\triangleright$ Confident containerising services and designing API's
    }
\headedsection
    {}
    {\textbf{Past Projects}}
    {
        $\triangleright$ A Chess Portable-Game-Notation Analysis Tool \\
        $\triangleright$ Events optimisation scheduling program with genetic algorithm \\
        $\triangleright$ Python web scraper to fetch events at local venue for
        family business. This allowed better planing and increased sales.
    }

\vspace{0.5em}
\hrule
\vspace{0.5em}

\hspace{-1.3em}\textbf{About Me}: I'm a boulderer. I'm closing in on a 1700 chess rating, and I love DnD

\end{document}
