\documentclass[12pt,twoside]{article}

\usepackage{geometry}
\usepackage{resume}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\begin{document}

\topheading
    {Adam Blackwater}
    {me@adamblackwater.com }
    {www.linkedin.com/in/adam-blackwater}
    {07722-432-866}
    {www.adamblackwater.com}
    {www.github.com/adam-blackwater}

\vspace{0.6em}
\hrule
\vspace{0.6em}

\statement
    {Personal Statement}
    {
        Software engineer with professional experience in back-end software
        development, and a university degree in Computer Science. Currently
        looking for a new role after previous employer ran out of money.

        \hspace{1.5em}Effective team member, thoroughly enjoy the
        collaborative aspect of software development. Good understanding of
        team building and how to deliver code. 

        \hspace{1.5em}Product minded and focused on creating value for both
        customers and business by contributing and collaborating.
    }

\vspace{0.8em}
\hrule
\vspace{0.8em}

\noindent{\textbf{Skills}}
\begin{center}
    \begin{tabular}{l l l l l l l}
        SQL & REST & AWS/GCP & cURL & Python & Redis & Micro services \\
        Git & TDD & CI/CD & Linux & aiohttp & Postgres & API design \& documentation \\
        SSH & Java & Kubernetes & HTTP & PyTest& Docker & Pair programming
    \end{tabular}
\end{center}
    
\parbox{35em}{
        $\triangleright$ Strong organisational skill developed while working my family's busines \\
        $\triangleright$ Proven to be a reliable team member and able to bring out the best in my team \\
        $\triangleright$ Used and enjoyed pair programming professionally to ship code 
    }

\vspace{0.8em}
\hrule
\vspace{0.8em}

\headedsection
    {Experience}
    {
        \textbf{WayHome} | Junior Back-End Software Engineer}
    {
        $\triangleright$ Developed containerised micro-services orchestrated using Kubernetes. \\
        $\triangleright$ Wrote services for consumption by the data team to aid
        in creating data models. \\
        $\triangleright$ Integrated third-party RESTful API's and wrote a service to
        automate a business process, freeing up valuable customer facing
        employee time.
    }

\vspace{0.8em}
\hrule
\vspace{0.8em}

\headedsection
    {Education}
    {
        \textbf{Computer Science; First-class honours | The University
        Greenwich: 2015 - 2019}
    }
    {
        $\triangleright$ Studied low level concepts (mathematical logic)
        through to high level - implemented a genetic combinatorial optimisation
        algorithm \\
        $\triangleright$ Won lead student representative role in first year.
        Chaired meetings, wrote a student review of the college for review by
        external observers.
    }

\vspace{0.7em}
\hrule
\vspace{0.7em}

\headedsection
    {Projects}
    {\textbf{A Chess Portable-Game-Notation (PGN) Analysis Tool} | \textit{Rust}}
    {
        $\triangleright$ Command line program that iterates over PGN files in a
        directory. \\
        $\triangleright$ Parses PGN files and returns win/loss/draws against
        opening moves played. \\
        $\triangleright$ Used TDD throughout development. \\
        $\triangleright$ Learnt Rust while developing this tool.
    }

\vspace{0.1em}

\headedsection
    {}
    {\textbf{Open Risk} | \textit{Python - aiohttp - MySql}}
    {
        $\triangleright$ Collaborating with others developers remotely \\
        $\triangleright$ Containerised using Docker \\
        $\triangleright$ Graph data structure for data modelling
    }

\vspace{0.7em}
\hrule
\vspace{0.7em}

\hspace{-2em}\textbf{About Me}: I'm a boulder, a chess player and I love DnD.

\end{document}

        %Product minded software engineer writing well tested code. Experience
        %writing RESTful APIs in Node.js + express, Python + Flask, and
        %using testing libraries.

        %\hspace{2.0em}Graduated with a first-class honours degree in Computer
        %Science at the end of 2019. Self-motivated and eager to turn my
        %experience of software engineering into products that create value for
        %both company and end user.

%\begin{center}
%        \begin{tabular}{c c}
%                Analytical Methods: \textbf{87\%} &
%                Artificial Intelligence: \textbf{83\%} \\
%                Advanced Programming: \textbf{82\%} &
%                Application and Web Development: \textbf{89\%} \\
%                Networking and Operating Systems: \textbf{99\%} &
%                Programming Distributed Components: \textbf{86\%} 
%        \end{tabular}
%\end{center}

%\headedsection
%    {}
%    {\textbf{Optimisation and Scheduling Software} | \textit{thesis}}
%    {
%        $\triangleright$ TTD based project using OOP principals. Used the MVC
%        design pattern. Made use of the Flask framework for front-end, and
%        Python for the back-end. \\
%        $\triangleright$ Applied a genetic combinatorial optimisation algorithm
%        to optimise a scheduling problem. \\
%        $\triangleright$ System read/writes MySQL database. Queries database,
%        result given to algorithm to automate schedule creation.
%    }
%

%$\triangleright$ Won lead student representative role in first year. Chaired meetings,
%        and took sole responsibility of producing a document for review by
%        senior staff and external observers.
